The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-04 analysis/paper/paper.qmd
Update top words and visualisation script in paper

```{r}
# Which are the top n most frequently used words in all theses?
get_top_words_per_corpus(data = emu_theses_words, top_n = 20)
```

<!-- ```{r} -->

<!-- # Which theses contain "fabric" in the top 20 most frequently used words? -->

<!-- emu_theses_top_20 %>%  -->

<!--   filter(word == "fabric") -->

<!-- emu_theses_top_20 %>% -->

<!--   slice(1:40) %>%  -->

<!--   ggplot(aes(x = reorder(word, n), y = n, fill = title)) + -->

<!--   geom_col() + -->

<!--   xlab(NULL) + -->

<!--   coord_flip() + -->

<!--   labs(y = "Count", -->

<!--        x = "Unique words", -->

<!--        title = "Count of unique words found in thesis", -->

<!--        subtitle = "Stop words were removed from the list") + -->

<!--   facet_wrap( ~ title, scales = "free", ncol = 2) -->

<!-- ``` -->

@@

spacyr::spacy_parse(emu_theses_bigrams$w_1)

>>>>

```{r}
# Which are the top n most frequently used words in all theses?
n = 20

# TODO add topic to fill aesthetic
get_top_words_per_corpus(data = emu_theses_words |> 
                           mutate(word = textstem::lemmatize_words(emu_theses_words$word)), top_n = n) |> 
  ggplot(aes(reorder(word, n), n)) +
  geom_col(fill = "orange") +
  geom_text(aes(label = n), size = 2, hjust = 1.1) +
  coord_flip() +
  xlab("Word") +
  ylab("Frequency") +
  labs(title = paste0("Top ", n, " most used words in the corpus of theses"))
  theme_minimal() +
  theme(panel.grid = element_blank())

@@

spacyr::spacy_parse(emu_theses_bigrams$w_1)
data.frame(emu_theses_bigrams$w_1, textstem::lemmatize_words(emu_theses_bigrams$w_1))

set.seed(12345)

# with spacy
extract_rand_window <- function(x, p){
    first_index = sample(seq(length(x) - p + 1), 1)
    x[first_index:(first_index + p -1)]
    }

example_lemma <-list()
for (i in 1:10) {
  example_lemma[[i]] <- extract_rand_window(emu_theses_bigrams$w_1,10)
}

Original <- unlist(example_lemma)
Lemmatized <- spacyr::spacy_parse(Original)

# with textstem
Lemmatized2 <- textstem::lemmatize_words(Original)

lemma_example <- data.frame(Original, Lemmatized2)

lemma_example

data.frame(Lemmatized$token, Lemmatized$lemma, Lemmatized2)
